
As people search online to plan trips or shop for new products, they frequently aim to collect evidence for potential options across multiple sources. Consider for example planning a trip: there may be hundreds of possible restaurants to dine at, attractions to see, and places to stay, each with corresponding evidence about its suitability for an individual's goals. Evidence about each option is often spread out across many webpages, including Yelp or TripAdvisor reviews, travel blogs, discussion forums, listicles, and travel guides. Further, each piece of evidence on its own may be susceptible to its creators' biases, context, and opinion, requiring users to synthesize across many pieces of evidence and entities to build a reliable landscape of the decision space.
Current browsers and note-taking software treat options and evidence mentioned in different webpages and in user notes as independent, which requires users to switch frequently between different browser tabs and their own notes for cross-referencing and foraging. As users collect more information, the costs of finding and organizing increases, making it difficult for users to keep track of what they are interested in and why. In my proposed work, I plan to.... 

\input{study1.tex}

\input{study2.tex}

\section{Evaluation and Contributions}

%I plan to conduct studies to explore this idea in two phases: First, a controlled lab study focusing on how this entity-centric approach can benefit foraging across webpages. I will use the findings from study 1 to inform the development and public release of a browser extension that supports both entity-centric foraging and structuring.

For Study 1, I will build a prototype system for a controlled lab study to explore the benefits and challenges of the entity-centric approach for reading, cross-referencing, and collecting information across multiple webpages in the browser. I plan to explore whether the gather- and propagate-based features can allow participants to cross-reference and re-access previously saved notes efficiently and whether participants consider having the additional features an improvement to their current methods.
Since note taking and bookmarking are longer term activities, for Study 2, I plan to publically release  a browser extension for Chrome (Figure \ref{fig:screenshot}) to reach a wider audience, collect usage information, and test the proposed approach in real-life settings. 

The core contribution of the proposed work is an entity-centric approach for supporting sensemaking across webpages in the browser when conducting complex exploratory search tasks, which includes:

\begin{itemize}
\item An extension that enables the browser to better understand the content of webpages by identifying entities using existing natural language processing algorithms and external knowledge sources (e.g., Wikipedia and Yelp), lowering the cost of cross-referencing different entities across webpages, searches, and external knowledge sources. 
\item A context-aware workspace where users can easily gather and structure options and evidence across multiple webpages, where relevant information saved previously will be resurfaced by the system as users browse different pages.
\end{itemize}

Equipping browsers and note-taking interfaces the ability to identify and connect options and evidence scattered across tabs and personal notes have the potentials of lowering the efforts required to make sense of and forage from many information sources. Empowering users to capture, associate, and structure fluidly their findings as they read and understand more information. Successes in doing so may also lead to useful insights on the design of future intelligent browser interfaces that can better understand the information being consumed by its users, and building novel interactive systems for supporting online sensemaking.


\section{Timeline and Submission Plans}

\subsection*{Timeline}

\begin{itemize}
    \item April - June 2019: Prototype Development
    \item June - August 2019: Deployment
    \item August - September 2019: Evaluation and Analysis
    \item October - December 2019: Write Dissertation and Defend 
\end{itemize}

\subsection*{Submission Plans}

\begin{itemize}
    \item ACM UIST 2019: \Cref{chap:fusion}
    \item ACM SIGCHI 2019: \Cref{chap:proposed}
\end{itemize}