
The previous chapter explore ways users can express and maintain their different criteria for selecting restaurants, and use them to visualize a review dataset and compare different search results. This chapter focus on supporting global context so that users can better evaluate their different options as they encountered them on different webpages. Unlike in the previous chapter where the evidence (i.e., reviews) were already recognized by the different restaurant entries on Yelp, this chapter instead support users' general browsing of different webpages using their browsers. This is enabled powering browsers with modern named entity recognition and linking algorithms, allowing us to identify the same entity mentioend across users' browser tabs.

As people research online to plan trips or shop for new products, they encounter many entities (e.g., attractions, products) and collect evidence across webpages to make informed decisions (e.g., reviews, listicles). Current browsers treat entities on each webpage independently of other pages, making it difficult for users to keep track of what they are interested in and why. We introduce Weaver, a novel browser add-on that weaves pages together through common entity mentions to support sensemaking across browser tabs in the context of trip planning. When users open a webpage, Weaver ``infuses'' it with evidence from other information sources relevant to entities on the current page. When users save notes, their notes are ``diffused'' across other pages that mentioned the same entity. We compared Weaver to a baseline and found participants utilized Weaver to gather nearly three times more evidence collected across significantly more webpages, and synthesized evidence to support decision making with lowered interaction costs.


\input{Chapters/Weaver/content.tex}

